### 2013-11-22 research/paper/results/results-2.3.tex
uploaded 22-11-2013 10.34 pm
Small changes to work from home

\JL{Up to here 12.20pm}

@@

>>>>

@@

\JL{KASUN: I don't understand the above paragraph. What is the main point of this paragraph? Are you trying to show that the only the terms dependent on $\dot{y}$ are dissipative, and so only those terms contribute to the transfer of energy or power to the body? That is true, but that is also true for VIV, so I don't see how that shows that the ``system is governed by the transverse velocity rather than the natural frequency''. I definitely don't understand that last sentence. Do you mean ``power'' when you say ``system''? The problem is that, as I've pointed out, the exact same argument regarding dissipation applies to VIV, which is strongly dependent on the natural frequency.}
